|

### 2024-10-15 posts/BarthPapageorgeThom/BPT.qmd
Completed BPT.html for RG2024/10/15

* Previous studies: EA scores $\SIM$ education
* This study: EA scores $\SIM$ wealth|education, parents
* EA scores $\SIM$ probabilistic thinking &rArr; human capital accumulation heterogeneity  
   * Teaching probability may make human capital more homogenous?
   * Not necessarily, gene-wealth gradient is a biased estimate &larr; environment
   * But it hints something can be done there

@@

こうした学習の遅れが格差の源泉と認識できるようになった

@@

* 「貧しさは遺伝する」?...PGSを使って資産との相関を計測した研究
* 強い根拠はないにせよ、介入ポイントを議論したのは素晴らしい
* Gene-wealth gradient = corr[PGS, wealth|(endogenous) variables]  
* 偏相関が小さくなるポイント: 株式所有 &lArr; longer time horizon, optimism
* 偏相関が大きくなるポイント: 確定給付年金
    * 株式所有と確定給付年金を加えたら偏相関は?
* 金融教育? 
* 確定給付年金をもっと広く手厚く(できるのか?)

>>>>

* Previous studies: $\corr$[EA scores, education]$>0$
* This study: $\corr$[EA scores, wealth|education, parents]$>0$
* EA scores $\SIM$ probabilistic thinking &rArr; human capital accumulation heterogeneity  
   * Teaching probability may make human capital more homogenous?
   * Not necessarily, gene-wealth gradient is a biased estimate &larr; environment
   * But it hints something can be done there

@@

こうした学習の遅れが格差の源泉の可能性、と認識できるようになった

@@

* 「貧しさは遺伝する」?...PGSを使って資産との相関を計測した研究
* 強い根拠はないにせよ、介入ポイントを議論したのは素晴らしい
* Gene-wealth gradient = $\corr$[PGS, wealth|(endogenous) variables]  
* 偏相関が小さくなるポイント: 株式所有 &lArr; longer time horizon, optimism
* 偏相関が大きくなるポイント: 確定給付年金
    * 株式所有と確定給付年金を加えたら偏相関は?
* 金融教育? 
* 確定給付年金をもっと広く手厚く(できるのか?)
* 計量: 個人固定効果の中身をPGSとそれ以外に分解
